Bip32-Ed25519++: A More Secure Hierarchical Deterministic Wallet Standard for Ed25519 Keys

### 2024-05-08 paper.tex
yareds corrections - remove unnecessary ineq
rephrase

\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
      \abstractText
      Implementing BIP32-style HD wallets for Ed25519 keys is a non-trivial task due to the non-linear key space of Ed25519. The paper BIP32-Ed25519 Hierarchical Deterministic Keys over a Non-linear Keyspace has seen wide adoption in the industry, but has some security issues. In this paper modifications are proposed that addresses those issues, at the cost of reducing the number of possible levels of child keys.
      \newline
      \newline
    \end{abstract}
  \end{@twocolumnfalse}
]

@@

The apostrophe in the paths indicates that the respective field is hardened, meaning that the child key is derived in a way that prevents the parent public key from being derived from the child public key, or the sibling keys of that child key. The derivation method is different for hardened keys, requiring the parent private key.

@@

 \begin{equation*}
  S = D - 1 = 2^{d} - 1 \leq 2^{g - 6}
  \end{equation*}

>>>>

\twocolumn[
  \begin{@twocolumnfalse}
    \maketitle
    \begin{abstract}
      \abstractText
      Implementing BIP32-style HD wallets for Ed25519 keys is a non-trivial task due to the non-linear key space of Ed25519. The paper BIP32-Ed25519 Hierarchical Deterministic Keys over a Non-linear Keyspace has seen adoption in the industry, but has some security issues. In this paper modifications are proposed that addresses those issues, at the cost of reducing the number of possible levels of child keys.
      \newline
      \newline
    \end{abstract}
  \end{@twocolumnfalse}
]

@@

The apostrophe in the paths indicates that the respective field is hardened, meaning that the child key is derived in a way that prevents the child public key from being derived publicly from the parent public key, or the sibling keys of that child key. The derivation method is different for hardened keys, requiring the parent private key.

@@

 \begin{equation*}
  S = D - 1 = 2^{d} - 1
  \end{equation*}
